
#< ignore
```{r "_"}
#library(restorepoint)
# facilitates error detection
#set.restore.point.options(display.restore.point=!TRUE)

library(RTutor)
library(yaml)
#library(restorepoint)
setwd("C:/Users/IngmarBuri/Desktop/RTutor")
ps.name = "SalienceEffects"; sol.file = paste0(ps.name,"_sol.Rmd")
libs = c("foreign", "dplyr", "ggplot2", "stargazer","lfe","readstata13") # character vector of all packages you load in the problem set
#name.rmd.chunks(sol.file) # set auto chunk names in this file
create.ps(sol.file=sol.file, ps.name=ps.name,user.name=NULL,libs=libs,stop.when.finished=FALSE, addons="quiz")
#traceback()
show.shiny.ps(ps.name, load.sav=FALSE,  sample.solution=FALSE, is.solved=FALSE, catch.errors=TRUE, launch.browser=TRUE)
stop.without.error()
```
#>

## Exercise 1 Overview

### Welcome!

This is an interactive RTutor worksheet that I have written in the course of my Bachelor thesis
at Ulm University. This worksheet will help you to reproduce and understand the results of the
research paper "Automatic Bill Payment and Salience Effects: Evidence from Electricity Consumption"
by Steven Sexton(first published May 2015 in Review of Economics and Statistics, Volume 97, Issue 2,
Page 229-241) which can be viewed and downloaded [here](http://www.mitpressjournals.org/doi/pdf/10.1162/REST_a_00465).
The study seeks to empirically assess whether Automatic Bill Payment(ABP) and Budget Billing(BB)
affect electricity consumption.
The datasets used by the author in this study contain monthly observations of residential and
commercial electricity consumers in South Carolina.


### __Structure__

**Exercise 1: Overview**

**Exercise 2: Introduction**

**Exercise 3: Getting to know the data**

**Exercise 4: All Residential Accounts**

**Exercise 5: Recent Residential Accounts**

**Exercise 6: Residential Energy Smart Accounts**

**Exercise 7: Residential Standard Accounts**

**Exercise 8: Resdiential Summer Conserving Accounts**

**Exercise 9: Residential Falsifications**

**Exercise 10: Residential Matched Falsifications**

**Exercise 11: Business Accounts**




## Exercise 2 -- Introduction

Let's start by looking at the dataset of all residential electricity consumers. The dataset is saved
in the file `Resdntal.dta`. To be able to work with the data it has to be read in first.
R provides many useful functions to read in data of various formats. To read `.dta` files though
you have to extend R's base functionality. Whenever you are missing some functionality in R, have a look
at the R package library (https://cran.r-project.org/). You can easily download packages from there
with the following syntax: `install.packages("package-name")`. To read a `.dta` file you need the function
`read.dta()`. It is part of the package `foreign`.


#< quiz "installing"
question: How would you install the package named `foreign`(don't forget the "" around the package name)?
answer: install.packages("foreign")
#>


This problemset already contains all required packages so you don't have to install any.
However to be able to use the functionality offered by an installed package you have to
make the code contained in the package accessible before every session with the command `library(package-name)`. Notice how the quotes
around the package-name argument for the function `library()` are not necessary (unlike for the function `install.packages()` from earlier).
In the following exercises you should not use quotes for the package-name argument of `library()`. If you do, your answer will not be recognized
as correct.

As you have already learned you need the function `read.dta()` from the package `foreign` to be able to read 
`.dta` files. The `read.dta()` function takes as argument the name of the file including the file ending `.dta`
in quotes. 
There is one last thing you have to know before you can start doing your first exercise.
You can assign data by writing `variable-name = ` followed by in our case a call to the
function `read.dta()`. This function will return data and it will be stored in the variable.

```{r "2_1"}
#< task
# Load the package foreign(make the code of the package accessible).

#>
library(foreign)
#< task
# Read and assign the data in the file Resdntal.dta to the variable res. Enter your code here:

#>
res = read.dta("Resdntal.dta")
#< hint
display("You assign the data you want to load to the variable res. You therefore write: res = ... Now you add read.dta(). In the parenthesis you write the 
name of the file you want to read. Don't forget to put quotes around the file name. Then click check.")
#>

```
#< award "Importing data is important!"
Great! You solved the first exercise and managed to import the data! Importing data is the first step on our way to analyze it.

There will be some awards to win in this problem set. You can easily look at them by typing `awards()` in the code box and click *run chunk*. 
#>

To get an idea about how the data looks like you can look at the head of the table with the command `head(data_name)`. Try it out if you want. 
<br>*You do not need to solve this exercise to be able to go on with the next task. Instead of using `head()` you can also click the button data*.

```{r "2_2",optional=TRUE}
#< task
# If you want you can look at the data with the head() command. Enter your code here:

#>
head(res)
```



## Exercise 3 -- Getting to know the data

Now that we have access to our data, we can try to check if ABP and BB really do have an effect on
electricity consumption and in which direction the effect goes. The assumption of the author is that it
should have an effect because both ABP and BB should reduce price salience. We can find out about the
size and the direction of the effect by running a regression. First we would like to know how the electricity
consumption, which is in the variable `ln_cons_per_day`, is affected by whether a consumer's electricity
bill is payed automatically. Whether that is the case was measured in the variable `abp`. In the dataset
`abp` is zero if the person was not enrolled in ABP at the time of the current billing period and 1 otherwise.
`abp` is therefore a dummy variable.

#< info "What is a dummy variable?"
A dummy variable is used to differentiate between two categories. The two categories are encoded with 1 and 0.
Gender for example can be stored in a dummy variable. Typically the name of the dummy variable is chosen
to be one of the two categories. The category that is chosen as name of the dummy variable will be encoded with 1
and the other category with 0. To make a dummy variable for gender you would name the variable `female` (`male`)
and encode `female` (`male`) as 1 and `male` (`female`) as 0.
The category that is encoded with 0 is called the base group.
The slope parameter of a dummy variable tells us how much higher or lower the dependent variable
is on average for the other group compared to the base group given that all other variables are fixed.

*Source: Wooldridge,Introductory Econometrics (2012), p.227 ff.,
from the free electronic version at: http://economics.ut.ac.ir/documents/3030266/14100645/Jeffrey_M._Wooldridge_Introductory_Econometrics_A_Modern_Approach__2012.pdf*
#>

To get an estimation of how much more electricity was on average consumed when bills were payed automatically
compared to manual payments we have to estimate this number statistically. We presume a linear relationship
between the variables `ln_cons_per_day` and `abp`.
This relationship can mathematically expressed in the folling way:
$$ln\_cons\_per\_day_{i} = \beta_{0} + \beta_{1} * abp_{i} + u_{i} $$

There are different ways to estimate a number for beta. We are going to use a method called
ordinary least squares(OLS) as the author did.


R has a built in function `lm()` that let's us do OLS regression. The syntax is as follows:
First you write the name of the independent variable on the left of the `~`-symbol. Then you write
the explanatory variable(s) on the right seperated by a `+`. Additionally you have to specify
the name of the data frame that contains the variables that are used in the regression.
In our case this amounts to.
`lm(ln_cons_per_day ~ abp,data=res)`.
Let's try this out:

```{r "3_1"}

#< task 
res=foreign::read.dta("Resdntal.dta")
# regression with abp:  
lm(ln_cons_per_day ~ abp,data=res)
#>
```

As you can see in the exercise you can also access a specific function of a package by writing
`package-name::function()`. This way you can use functions of packages without having to call
`library(package-name)` beforehand. In this sessions we have called `library(foreign)` already. So `read.dta()`
would have worked without `foreign::` .

```{r "3_2"}
#< task
# regression with bb
# do the same regression but instead of abp use bb: Replace the ???
# and then delete the # sign before you click check
# lm(ln_cons_per_day ~ ???,data=res)

#>
lm(ln_cons_per_day ~ bb,data=res)
#< hint
display("Make sure you have deleted the # sign!")
#>
```

As you can see the result is not quite as one would expect. Being part of the abp
program does not seem to raise electricity consumption. But taking part in bb does increase
electricity consumption. Taking part in either of these programs should increase electricity 
consumption.
These results can't be trusted however as they suffer strongly from omitted variable bias which
means that there are many other things that influence abp or bb which we haven't incorporated
in our regression yet. The following regressions contain the most important other influence
factors and should therefore be a more accurate estimate of the true effect. We are going to 
use the function `felm` from the `lfe` package for the following regressions.


## Exercise 4 -- All Residential Accounts

You have already run a simple linear regression on the dataset that contains
observations of all (and only) residential electricity consumers. On the same dataset we 
are going to run the regressions the author ran. As you can see they contain
more variables to account for other influences that should have an affect on 
electricity consumption as well.

```{r "4_1"}
#< task 
res=foreign::read.dta("Resdntal.dta")
# slim down the dataset by chosing all variables that we need
# and drop the remaining variables
res = dplyr::select(res,ln_cons_per_day,abp,bb,abp_X_bb_ever,
                       bb_X_abp_ever,acct_seq,
                       acct_seq_X_abp_ever,acct_seq2,acct_seq3,
                       year_month,month,zip5,id_rate_code)
#>
```

```{r "4_2"}
#< task 

felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                     as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                   exactDOF = TRUE,data=res)
#>
```

```{r "4_3"}
#< task 

felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res)
#>
```

Great now the next step is to display our regression results in a nice formatted way.
The package `stargazer` can be used for this.

```{r "4_4",results='asis'}
#< task 
# Display the regression results stored in felm1 and felm2 in one table.
library(stargazer)
stargazer(felm1,felm2,type="html",digits=8)
#>
```


## Exercise 5 -- Recent Residential Accounts

In this exercise we are going to run the same regressions as in exercise 4 
but on a subset of the dataset that we used there. Here we look only at observations
of accounts that were initiated in the year 2000 or later. These observations
are in the file `rsd_recent.dta`.


```{r "5_1"}
#< task 
res_recent = read.dta("rsd_recent.dta")
#>
```

```{r "5_2"}
#< task 

rec_felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                     as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                   exactDOF = TRUE,data=res_recent)
#>
```

```{r "5_3"}
#< task 

rec_felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_recent)
#>
```

```{r "5_4",results='asis'}
#< task 
# Now display the regression results stored in rec_felm1 and rec_felm2
# in one table. Look at exercise 4 if you have forgotten how to do it.
# The precision should be 8 digits like before.

#>
stargazer(rec_felm1,rec_felm2,type="html",digits=8)
```

## Exercise 6 -- Residential Energy Smart Accounts

This data looks only at residential consumers who are in the rate class for new and
retrofitted energy-efficient homes.

```{r "6_1_1"}
#< task 
res_en_sm = read.dta("ResEnSm.dta")

felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                     as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                   exactDOF = TRUE,data=res_en_sm)
#>
```

```{r "6_1_2"}
#< task 

felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_en_sm)
#>
```

```{r "6_1_3",results='asis'}
#< task 
# Display the regression results stored in felm1 and felm2 in one table.
stargazer(felm1,felm2,type="html",digits=8)
#>
```

```{r "6_2_1"}
#< task 
res_en_sm_rec = read.dta("res_en_sm_rec.dta")

rec_felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_en_sm_rec)
#>
```

```{r "6_2_2"}
#< task 

rec_felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_en_sm_rec)
#>
```

```{r "6_2_3",results='asis'}
#< task 
# Now display the regression results stored in rec_felm1 and rec_felm2
# in one table. 
stargazer(rec_felm1,rec_felm2,type="html",digits=8)
#>
```

## Exercise 7 -- Residential Standard Accounts

This data looks only at residential consumers who are in the standard rate class.

```{r "7_1_1"}
#< task 
res_std = read.dta("ResStd.dta")

felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                     as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                   exactDOF = TRUE,data=res_std)
#>
```

```{r "7_1_2"}
#< task 

felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_std)
#>
```

```{r "7_1_3",results='asis'}
#< task 
# Display the regression results stored in felm1 and felm2 in one table.
stargazer(felm1,felm2,type="html",digits=8)
#>
```

```{r "7_2_1"}
#< task 
res_std_rec = read.dta("res_std_rec.dta")

rec_felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_std_rec)
#>
```

```{r "7_2_2"}
#< task 

rec_felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_std_rec)
#>
```

```{r "7_2_3",results='asis'}
#< task 
# Now display the regression results stored in rec_felm1 and rec_felm2
# in one table. 
stargazer(rec_felm1,rec_felm2,type="html",digits=8)
#>
```

## Exercise 8 -- Residential Summer Conserving Accounts

This data looks only at residential consumers who are in the summer conserving rate
class. Consumers in this rate class have a discounted rate but in exchange for that undertake to consume
maximally as much as a value that is determined relative to own winter consumption.

```{r "8_1_1"}
#< task 
res_summ_cons = read.dta("ResSummerCons.dta")

felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                     as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                   exactDOF = TRUE,data=res_summ_cons)
#>
```

```{r "8_1_2"}
#< task 
 
felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_summ_cons)
#>
```

```{r "8_1_3",results='asis'}
#< task 
# Display the regression results stored in felm1 and felm2 in one table.
stargazer(felm1,felm2,type="html",digits=8)
#>
```

```{r "8_2_1"}
#< task 
res_summcon_rec = read.dta("res_summ_cons_rec.dta")
 
rec_felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                exactDOF = TRUE,data=res_summcon_rec)
#>
```

```{r "8_2_2"}
#< task  

rec_felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=res_summcon_rec)
#>
```

```{r "8_2_3",results='asis'}
#< task 
# Now display the regression results stored in rec_felm1 and rec_felm2
# in one table. 
stargazer(rec_felm1,rec_felm2,type="html",digits=8)
#>
```

## Exercise 9 -- Residential Falsifications



```{r "9_1_1"}
#< task 
res=read.dta("Resdntal.dta")

felm1=lfe::felm(ln_cons_per_day~pseudo_abp_13+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=filter(res,abp_centered_date <= -1 | is.na(abp_centered_date)))
#>
```

```{r "9_1_2"}
#< task 

felm2=lfe::felm(ln_cons_per_day~pseudo_abp_16+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=filter(res,abp_centered_date <= -1 | is.na(abp_centered_date)))
#>
```

```{r "9_1_3"}
#< task 

felm3=lfe::felm(ln_cons_per_day~pseudo_abp_19+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=filter(res,abp_centered_date <= -1 | is.na(abp_centered_date)))
#>
```

```{r "9_1_4"}
#< task 

felm4=lfe::felm(ln_cons_per_day~pseudo_abp_22+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=filter(res,abp_centered_date <= -1 | is.na(abp_centered_date)))
#>
```

```{r "9_1_5"}
#< task 
 
felm5=lfe::felm(ln_cons_per_day~pseudo_abp_25+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=filter(res,abp_centered_date <= -1 | is.na(abp_centered_date)))
#>
```

Great now the next step is to display our regression results in a nice formatted way.

```{r "9_1_6",results='asis'}
#< task 
# Display the regression results stored in felm1 and felm2 in one table.
stargazer(felm1,felm2,felm3,felm4,felm5,type="html",digits=8)
#>
```

## Exercise 10 -- Residential Matched Falsifications



```{r "10_1_1"}
#< task 
res_fa_ma=read.dta("ResFaMa.dta")

felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=filter(res_fa_ma,abp_centered_date <= -1 | is.na(abp_centered_date)))
#>
```

Great now the next step is to display our regression results in a nice formatted way.
As you should know now, the package `stargazer` can be used for this.

```{r "10_1_2",results='asis'}
#< task 
# Display the regression results stored in felm1.
stargazer(felm1,type="html",digits=8)
#>
```

## Exercise 11 -- Business Accounts

In this exercise we are going to analyse a dataset that contains business accounts exclusively.

```{r "11_1_1"}
#We need another function to read in this `.dta` file since
#this `.dta` file is slightly different than the other `.dta` files
#that we have read in so far.
#< task 
library(readstata13)
business = read.dta13("Business.dta")

felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                     as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                   exactDOF = TRUE,data=business)
#>
```
```{r "11_1_2"}
#< task 
 
felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=business)
#>
```
Great now the next step is to display our regression results in a nice formatted way.
As you should know now, the package `stargazer` can be used for this.

```{r "11_1_3",results='asis'}
#< task 
# Display the regression results stored in felm1 and felm2 in one table.
stargazer(felm1,felm2,type="html",digits=8)
#>
```

```{r "11_2_1"}
#< task 
business_rec = readstata13::read.dta13("Business_rec.dta")
 
rec_felm1=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code),
                exactDOF = TRUE,data=business_rec)
#>
```

```{r "11_2_2"}
#< task 

rec_felm2=lfe::felm(ln_cons_per_day~abp+bb+abp_X_bb_ever+bb_X_abp_ever+
                  acct_seq+acct_seq_X_abp_ever+acct_seq2+acct_seq3 | 
                  as.factor(year_month) + as.factor(month) + 
                  as.factor(month):as.factor(zip5) + as.factor(zip5)+
                  as.factor(id_rate_code) | 0 | zip5,
                exactDOF = TRUE,data=business_rec)
#>
```

```{r "11_2_3",results='asis'}
#< task 
# Now display the regression results stored in rec_felm1 and rec_felm2
# in one table.
stargazer(rec_felm1,rec_felm2,type="html",digits=8)
#>
```
